\textbf{ Accurate spectrophotometric estimates of luminosity and distance\\ for luminous red-giant stars }

### 2018-07-30 paper/sp.tex
A/B split

HOGG: PUT WORDS HERE ABOUT GOING TWO-FOLD to pre-flash that we are going to do that
in the next Section.

>>>>

One final detail: We perform all of the fitting in a two-fold train-and-test framework,
in which the data are split into two disjoint subsets, A and B.
The model trained on the A data is used to predict the $Q_m$ values (and hence
the luminosities, distances, and parallaxes) of the B data,
and the model trained on the B data is used to 
predict the $Q_m$ values of the A data.
This ensures that, in the estimate of any individal star's luminosity, distance,
or parallax, none of the \gaia\ data pertaining to that star was used.
This makes the parallax estimates from the spectrophotometric feature vectors
$x_m$ statistically independent of the \gaia\ parallax measurements.
They are not independent \emph{globally}, but they are independent on a
star-by-star basis.
